RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2013-12-17 papers/rjournal/eddelbuettel-francois-stokely.Rnw
Add some new boilerplate for sections describing the basic abstractions and basic classes of RProtoBuf.  Also, make the first example more concise by putting the example .proto file and example R session using it side by side (before we go into full detail about all the accessors in RProtoBuf, this just gives a preview)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@563 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;        // Unique ID number for person.
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1; WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2 [default = HOME];
 }
 repeated PhoneNumber phone = 4;
}
\end{example}

<<echo=TRUE>>=
library(RProtoBuf)
person <- new(tutorial.Person, id=1, name="Romain")
person$id
person$name
person$name <- "Dirk"
cat(as.character(person))
@

@@

\emph{TODO(mstokely): Remove this example code snippet}

\begin{example}
  x <- 1:10
  result <- myFunction(x)
\end{example}

@@

\section{64-bit integer issues}
\label{sec:int64}

>>>>

\noindent
\begin{tabular}{@{}p{.40\textwidth}|p{0.5\textwidth}@{}}
\begin{minipage}{.35\textwidth}
\begin{example}
package tutorial;
message Person {
 required string name = 1;
 required int32 id = 2;
 optional string email = 3;
 enum PhoneType {
   MOBILE = 0; HOME = 1;
   WORK = 2;
 }
 message PhoneNumber {
   required string number = 1;
   optional PhoneType type = 2;
 }
 repeated PhoneNumber phone = 4;
}
\end{example}
\end{minipage} & \begin{minipage}{.45\textwidth}
<<echo=TRUE>>=
library(RProtoBuf)
person <- new(tutorial.Person, id=1,
              name="Romain")
person
person$name
person$name <- "Dirk"
cat(as.character(person))
@ 
\end{minipage}
\end{tabular}

@@

@@

\section{Basic Abstractions: Messages, Descriptors, and
  DescriptorPools}

The three basic abstractions of \CRANpkg{RProtoBuf} are Messages,
which encapsulate a data structure, Descriptors, which define the
schema used by one or more messages, and DescriptorPools, which
provide access to descriptors.

\section{Under the hood: S4 Classes, Methods, and Pseudo Methods}

The \CRANpkg{RProtoBuf} package uses the S4 system to store
information about descriptors and messages, but the information stored
in the R object is very minimal and mainly consists of an external
pointer to a C++ variable that is managed by the \texttt{protobuf} C++
library.

Using the S4 system allows the \texttt{RProtoBuf} package to dispatch
methods that are not generic in the S3 sense, such as \texttt{new} and
\texttt{serialize}.

The \texttt{RProtoBuf} package combines the \emph{R typical} dispatch
of the form \verb|method( object, arguments)| and the more traditional
object oriented notation \verb|object$method(arguments)|.

TODO(ms): Perhaps a table here of the different S4 classes, how many
methods they include, whether it dynamically does dispatch on other
strings, whether/how it is available in the search path, etc.

\subsection{Messages}

The \texttt{Message} S4 class represents Protocol Buffer Messages and
is the core abstraction of \CRANpkg{RProtoBuf}.  Each \texttt{Message}
has a \texttt{Descriptor} S4 class which defines the schema of the
data defined in the Message, as well as a number of
\texttt{FieldDescriptors} for the individual fields of the message.

represented in R using the \texttt{Message}
S4 class. The class contains the slots \texttt{pointer} and \texttt{type} as
described on the Table~\ref{Message-class-table}.

\section{Type Coercion}

\subsection{Booleans}
Bools
Int64s.

\subsection{64-bit integers}
\label{sec:int64}
